Implementation of poloidal density variation in collision operator

### 2018-04-17 doc/manual/version3/inputParameters.tex
added sfincsScan22

{\ttfamily scanType} = 21: Read in a list of requested runs from a
file {\ttfamily runspec.dat}. See
\path{sfincs/fortran/utils/sfincsScan_21} for an example file. If the
file has a different name than {\ttfamily runspec.dat}, for instance
{\ttfamily thefilename.dat}, this name can be
specified by adding the line\\
{\ttfamily
!ss runSpecFile = thefilename.dat\\
}
}

>>>>

{\ttfamily scanType} = 21: Read in a list of requested runs from a
file {\ttfamily runspec.dat}. See
\path{sfincs/fortran/utils/sfincsScan_21} for an example file. If the
file has a different name than {\ttfamily runspec.dat}, for instance
{\ttfamily thefilename.dat}, this name can be
specified by adding the line\\
{\ttfamily
!ss runSpecFile = thefilename.dat\\}

{\ttfamily scanType} = 22: Similar to {\ttfamily scanType}=5 but the
radial scan is specified with a runspec file like for {\ttfamily
  scanType}=21. For each line in the {\ttfamily runspec.dat} file a
directory is created, in which a {\ttfamily scanType}=2 $E_r$ scan is started.\\
}
